Spatial and temporal variability in economic availability of residual biomass

### 2021-11-21 analysis/manuscript.Rmd
tiffs gone

Another product of NFIS is a set of spatial datasets derived from
satellite data @NFIS2021b.  The dataset used for this study is the
harvest year data set for the years 1985-2015.  The dataset is
described in detail by Hermosilla *et al.*  @Hermosilla2016.  It
consists of a raster for Canada at 30 m resolution indicating the year
of harvest for each cell.

The NFIS also provides a web-based individual tree biomass calculator
@NFIS2021a.  It is used to calculate stem wood, stem bark, branch, and
foliage biomass for a tree based on province, ecozone, species,
diameter at breast height (DBH) and height.  It is possible to upload
a file representing many trees with different combinations of these
input parameters and download a file containing the calculated results
for all the trees.

@@

The boundaries of Canada's terrestrial ecozones can be found on
Agriculture and Agri-Food Canada's website @Canada2017.  Ecozone is an
input to the individualt tree biomass calculator @NFIS2021.

@@

The areas harvested by township in 2009 according to NFIS @NFIS2021b
@Hermosilla2016 are shown in relationship to the three plant locations and 
the Green Area in Figure 1.  Similar aggregated data were created for
each of the years 1990--2015. For each township, and
each of the years between 1990 and 2015, we store the area harvested (ha) for
use in our analysis.  We can see from this map that a great deal of timber
harvest took place near our hypothetical plant locations in 2009.

These data were created by using QGIS zonal statistics to sum the area
harvested in each township in each year based on the 30 m resolution
harvest data @NFIS2021b.

@@

Canada's national forest inventory website provides a useful individual
tree biomass calculator @NFIS2016.  It calculates the biomass of tree 
components (stem wood, stem bark, branches, foliage, and total) using
province/territory, terrestrial ecozone, species, DBH, and tree height as input.
It is possible to upload a file to the calculator so that the biomass of
many trees can be calculated at once.  The calculator is based on work
by Lambert *et al.* @Lambert2005.

@@

ggsave("../img/harv_comparison.tiff", plot = harv_comparison, device='tiff', dpi=300)

@@

ggsave("../img/cyclePlot.tiff", plot = cyclePlot, device='tiff', dpi=300)

@@

ggsave("../img/mcPlot.tiff", plot = mcPlot, device='tiff', dpi=300)

@@

ggsave("../img/bPlot.tiff", plot = bPlot, device='tiff', dpi=300)

@@

#ggsave("../img/avePlot.tiff", plot = avePlot, width = 6, height = 4, units = "in", device='tiff', dpi=300)
ggsave("../img/avePlot.tiff", plot = avePlot, device='tiff', dpi=300)

>>>>

Another product of NFIS is a set of spatial datasets derived from
satellite data @NFIS2021a.  The dataset used for this study is the
harvest year data set for the years 1985-2015.  The dataset is
described in detail by Hermosilla *et al.*  @Hermosilla2016.  It
consists of a raster for Canada at 30 m resolution indicating the year
of harvest for each cell.

The NFIS also provides a web-based individual tree biomass calculator
@NFIS2021b.  It is used to calculate stem wood, stem bark, branch, and
foliage biomass for a tree based on province, ecozone, species,
diameter at breast height (DBH) and height.  It is possible to upload
a file representing many trees with different combinations of these
input parameters and download a file containing the calculated results
for all the trees.

@@

The boundaries of Canada's terrestrial ecozones can be found on
Agriculture and Agri-Food Canada's website @Canada2017.  Ecozone is an
input to the individualt tree biomass calculator @NFIS2021b.

@@

The areas harvested by township in 2009 according to NFIS @NFIS2021a
@Hermosilla2016 are shown in relationship to the three plant locations and 
the Green Area in Figure 1.  Similar aggregated data were created for
each of the years 1990--2015. For each township, and
each of the years between 1990 and 2015, we store the area harvested (ha) for
use in our analysis.  We can see from this map that a great deal of timber
harvest took place near our hypothetical plant locations in 2009.

These data were created by using QGIS zonal statistics to sum the area
harvested in each township in each year based on the 30 m resolution
harvest data @NFIS2021a.

@@

Canada's national forest inventory website provides a useful individual
tree biomass calculator @NFIS2021b.  It calculates the biomass of tree 
components (stem wood, stem bark, branches, foliage, and total) using
province/territory, terrestrial ecozone, species, DBH, and tree height as input.
It is possible to upload a file to the calculator so that the biomass of
many trees can be calculated at once.  The calculator is based on work
by Lambert *et al.* @Lambert2005.

@@

ggsave("../img/harv_comparison.png", plot = harv_comparison, device='png', dpi=300)

@@

ggsave("../img/cyclePlot.png", plot = cyclePlot, device='png', dpi=300)

@@

ggsave("../img/mcPlot.png", plot = mcPlot, device='png', dpi=300)

@@

ggsave("../img/bPlot.png", plot = bPlot, device='png', dpi=300)

@@

#ggsave("../img/avePlot.png", plot = avePlot, width = 6, height = 4, units = "in", device='png', dpi=300)
ggsave("../img/avePlot.png", plot = avePlot, device='png', dpi=300)
